Application-Level Regression Testing Framework using Jenkins

### 2017-03-30 manuscript/manuscript.tex
Disabled long abstract and inca ref
line feeds enabled some sections that were hidden before. That text can
be used in any section if needed.

Pwauth is called by \texttt{/etc/htpd/conf.d/authnz_external.conf}: 
\begin{lstlisting}
LoadModule authnz_external_module modules/mod_authnz_external.so
DefineExternalAuth pwauth pipe /usr/bin/pwauth
DefineExternalAuth pwauth+sssion pipe /usr/local/bin/pwauth+session
\end{lstlisting}

@@

%\subsection{Security Considerations}
%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. 
Blue Waters is an OTP only restricted access system. 
Jenkins has the ability to execute user-level commands on our login nodes. 
It also has some unfortunate default settings. 
The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. 
Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance. 
 This required us initially to test the deployment with our TDS. 
This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. 
In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space. 
 The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

@@

% references section
\section*{References}
[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
[2] https://jenkins.io/ Jenkins: open source automation server written in Java

>>>>

Pwauth is called by \texttt{/etc/htpd/conf.d/authnz_external.conf}: 
\begin{lstlisting}
LoadModule authnz_external_module \
modules/mod_authnz_external.so
DefineExternalAuth pwauth pipe /usr/bin/pwauth
DefineExternalAuth pwauth+sssion pipe \
/usr/local/bin/pwauth+session
\end{lstlisting}

@@

%\subsection{Security Considerations}
%CUT THE NEXT TWO PARAGRAPHS AND DESCRIPTION OF CONFIG FILES OR REDUCE SINCE IT IS COVERED ABOVE --GALEN
%Enabling Jenkins access to Blue Waters posed some unique security hurdles that we had to overcome. 
%Blue Waters is an OTP only restricted access system. 
%Jenkins has the ability to execute user-level commands on our login nodes. 
%It also has some unfortunate default settings. 
%The access control is set to "Jenkins' own user database," and the "Allow users to sign up" option is enabled, so if you don't have an account, you can create one by providing your name, e-mail and a password. 
%Additionally, there's an authorization option enabled which says "Logged-in users can do anything." So, once signed in, you have full admin access to the Jenkins system instance. 
% This required us initially to test the deployment with our TDS. 
%This resulted in the following requirement: restricted OTP access to the physical system hosting Jenkins. 
%In addition, OTP only access to the Jenkins GUI command console must be contained within our IP space. 
% The Jenkins GUI will also restrict the command console access to our Blue Waters LDAP server.

@@

% references section
\section*{References}
%[1] http://inca.sdsc.edu/ Inca Monitoring: periodic, automated, user-level cyberinfrastructure testing
[1] https://jenkins.io/ Jenkins: open source automation server written in Java
